\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-03-27 paper.qmd
Amend starting point description

```{r}
#| echo: false
#| fig-cap: "(a) Visualization of bin centroids and (b) hexagonal grid, showcasing the configuration before (colored in gray) and after (colored in light orange) shifting the starting point by an identical amount applied in both x and y directions, with a shift value of $0.537285$."
#| label: fig-scurveshifthexgridsexp
#| fig-pos: H

@@

```{r}
#| echo: false
#| fig-cap: "Hexbin plots shows the distribution of points before and after shifting the starting point of the hexagonal grid generated for UMAP applied to the training S-curve dataset. (a) Hexbin plot before shifting, and (b) Hexbin plot after shifting (identical shift applied in both x and y directions, with a shift value of $0.537285$)."
#| label: fig-scurveshifthexgrids
#| fig-pos: H

>>>>

```{r}
#| echo: false
#| fig-cap: "(a) Visualization of bin centroids and (b) hexagonal grid, showcasing the configuration when the starting point defined at $(-0.113, -0.098)$ (colored in gray) and the starting point defined at $(-0.025, -0.108)$ (colored in light orange)."
#| label: fig-scurveshifthexgridsexp
#| fig-pos: H

@@

```{r}
#| echo: false
#| fig-cap: "Hexbin plots shows the distribution of points before and after changing the starting point of the hexagonal grid generated for UMAP applied to the training S-curve dataset. (a) Hexbin plot when the starting point defined at $(-0.113, -0.098)$, and (b) Hexbin plot after changing the starting point to $(-0.025, -0.108)$."
#| label: fig-scurveshifthexgrids
#| fig-pos: H

### 2024-03-27 paper.tex
Amend starting point description

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, frame hidden, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\caption{\label{fig-scurveshifthexgridsexp}(a) Visualization of bin
centroids and (b) hexagonal grid, showcasing the configuration before
(colored in gray) and after (colored in light orange) shifting the
starting point by an identical amount applied in both x and y
directions, with a shift value of \(0.537285\).}

@@

\caption{\label{fig-scurveshifthexgrids}Hexbin plots shows the
distribution of points before and after shifting the starting point of
the hexagonal grid generated for UMAP applied to the training S-curve
dataset. (a) Hexbin plot before shifting, and (b) Hexbin plot after
shifting (identical shift applied in both x and y directions, with a
shift value of \(0.537285\)).}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, boxrule=0pt, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

\caption{\label{fig-scurveshifthexgridsexp}(a) Visualization of bin
centroids and (b) hexagonal grid, showcasing the configuration when the
starting point defined at \((-0.113, -0.098)\) (colored in gray) and the
starting point defined at \((-0.025, -0.108)\) (colored in light
orange).}

@@

\caption{\label{fig-scurveshifthexgrids}Hexbin plots shows the
distribution of points before and after changing the starting point of
the hexagonal grid generated for UMAP applied to the training S-curve
dataset. (a) Hexbin plot when the starting point defined at
\((-0.113, -0.098)\), and (b) Hexbin plot after changing the starting
point to \((-0.025, -0.108)\).}
